Evaluating contact tracing and isolation to control pandemic potential influenza outbreaks

### 2025-04-14 inst/paper/main.tex
add onset-to-isolation plot to paper and re-render pdf

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{../plots/prop_outbreak_control_onset_to_isolation.png}
\caption{The percentage of outbreaks controlled across values of contact and isolation effectiveness, for outbreaks with an onset-to-isolation delay distribution that is either SARS-like, or COVID-19-like (from Wuhan). This is for a baselines scenario where the reproduction number is 1.5, the proportion of presymptomatic transmission is 15\%, all cases are assumed symptomatic, and the number of initial infections is 10.}
\label{fig:prop-outbreak-control-onset-to-isolation}
\end{figure}
